Virtualisierung eines Echtzeit-Betriebssystems zur Steuerung eines Roboters mit Schwerpunkt auf die Einhaltung der Echtzeit

### 2024-08-09 Masterarbeit_Robotik_Pamuk.tex
PW 022 three times

\chapter{Real-Time Robotic Application}\label{cha:real-time-testing}
This chapter compares the latency of the Salamander 4 operating system before and after the real-time performance tunings. Additionally, these results are contrasted with the latency of Salamander 4 running on bare metal hardware to understand how closely the performance of the virtualization can match that of the bare metal. The experimental setup includes a six-axis mini-robot, illustrated in Figure \ref{fig:mini_robot}.

@@

	exec taskset -c 4 qemu-system-x86_64 -M pc,accel=kvm -kernel ./bzImage \
	-m 2048 -drive file=salamander-image-sigmatek-core2.ext4,format=raw,media=disk \
	-append "console=ttyS0 console=tty1 root=/dev/sda rw panic=1 sigmatek_lrt.QEMU=1 ip=dhcp rootfstype=ext4 schedstats=enable nohlt idle=poll quiet xeno_hal.smi=1 xenomai.smi=1 threadirqs" \
	-net nic,model=e1000,netdev=e1000 -netdev bridge,id=e1000,br=nm-bridge \
	-fsdev local,security_model=none,id=fsdev0,path=drive-c -device virtio-9p-pci,id=fs0,fsdev=fsdev0,mount_tag=/mnt/drive-C \
	-device vhost-vsock-pci,guest-cid=3,id=vsock0 \
	-drive if=pflash,format=qcow2,file=ovmf.code.qcow2 \
	-object memory-backend-ram,id=ram0,size=4G,prealloc=on \
	-mem-prealloc -mem-path /dev/hugepages \
	-device vfio-pci,host=03:00.0 \
	-no-reboot -nographic
\end{lstlisting}
\end{minipage}

>>>>

\chapter{Real-Time Robotic Application}\label{cha:real-time-testing}
This chapter compares the latency of the Salamander 4 operating system before and after the real-time performance tunings with the latency of Salamander 4 running on bare metal hardware. This comparison is done with the aid of a program that will be explained shortly. The goal is to understand how closely the performance of the virtualization can match that of the bare metal. The experimental setup includes a six-axis mini-robot, illustrated in Figure \ref{fig:mini_robot}.

@@

	exec taskset -c 4-5 chrt -f 99 qemu-system-x86_64 -M pc,accel=kvm -kernel ./bzImage \
	-m 2048 -drive file=salamander-image-sigmatek-core2.ext4,format=raw,media=disk \
	-append "console=ttyS0 console=tty1 root=/dev/sda rw panic=1 sigmatek_lrt.QEMU=1 ip=dhcp rootfstype=ext4 schedstats=enable nohlt idle=poll quiet xeno_hal.smi=1 xenomai.smi=1 threadirqs" \
	-net nic,model=e1000,netdev=e1000 -netdev bridge,id=e1000,br=nm-bridge \
	-fsdev local,security_model=none,id=fsdev0,path=drive-c -device virtio-9p-pci,id=fs0,fsdev=fsdev0,mount_tag=/mnt/drive-C \
	-device vhost-vsock-pci,guest-cid=3,id=vsock0 \
	-drive if=pflash,format=qcow2,file=ovmf.code.qcow2 \
	-object memory-backend-ram,id=ram0,size=4G,prealloc=on \
	-mem-prealloc -mem-path /dev/hugepages \
	-device vfio-pci,host=03:00.0 \
	-no-reboot -nographic
\end{lstlisting}
\end{minipage}
